Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-07-25 replication_paper/pnas_draft/appendix.Rmd
path update

library(reticulate)
reticulate::py_discover_config()
#use_python("/home/skynet3/anaconda3/bin/python/")
#reticulate::use_python("/home/tlscherer/anaconda3/bin/python")

@@

import torch
use_cuda = torch.cuda.is_available()
if use_cuda:
    print('__CUDNN VERSION:', torch.backends.cudnn.version())
    print('__Number CUDA Devices:', torch.cuda.device_count())
    print('__CUDA Device Name:',torch.cuda.get_device_name(0))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
    print('__CUDA Device Name:',torch.cuda.get_device_name(1))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)

import random
import os
from tqdm.auto import tqdm
import pandas as pd
from transformers import pipeline
from transformers.pipelines.pt_utils import KeyDataset

@@

fromscratch=F
if(fromscratch){
  raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value_normalized) %>% distinct()

>>>>

library(reticulate)
reticulate::py_discover_config()
#use_python("/home/skynet3/anaconda3/bin/python/")
#reticulate::use_python("~/anaconda3/bin/python3.6") # never worked for me
#reticulate::use_python("~/.local/share/r-miniconda/envs/r-reticulate/bin/python3.6") #works but needed module install
#conda_install("r-reticulate", "pytorch")

@@

if fromscratch:
  import torch
  use_cuda = torch.cuda.is_available()
  if use_cuda:
      print('__CUDNN VERSION:', torch.backends.cudnn.version())
      print('__Number CUDA Devices:', torch.cuda.device_count())
      print('__CUDA Device Name:',torch.cuda.get_device_name(0))
      print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
      print('__CUDA Device Name:',torch.cuda.get_device_name(1))
      print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)    
  import random
  import os
  from tqdm.auto import tqdm
  import pandas as pd
  from transformers import pipeline
  from transformers.pipelines.pt_utils import KeyDataset

@@

fromscratch=F
if(fromscratch){
  raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value) %>% distinct()
